---
title: "Analysis Example of Bayesian MCPMod for Continuous Data"
output: rmarkdown::html_vignette
number_sections: true
vignette: >
  %\VignetteIndexEntry{Analysis Example of Bayesian MCPMod for Continuous Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BayesianMCPMod)
library(clinDR)
library(dplyr)

set.seed(7015)
```
# Background and data

In this vignette we will show the use of the Bayesian MCPMod package for continuous distributed data. 
Hereby the focus is on the utilization of an informative prior and the BayesianMCPMod evaluation of a single trial.
We will use data that is included in the clinDR package. 
More specifically trial results for BRINTELLIX will be used to illustrate the specification of an informative prior and the usage of such a prior for the bayesian evaluation of a (hypothetical) new trial. 
More information around BRINTELLIX will be added...


# Calculation of a MAP prior
In a first step a meta analytic prior will be calculated using historical data from 4 trials (with main endpoint CfB in MADRS score after 8 weeks).
Please note that only information from the control group will be integrated (leading to an informative multicomponent prior for the control group), while for the active groups a non-informative prior will be specified.
```{r Calculation of a MAP prior}
data("metaData")
testdata    <- as.data.frame(metaData)
dataset     <- filter(testdata, bname == "BRINTELLIX")
histcontrol <- filter(dataset, dose == 0, primtime == 8, indication == "MAJOR DEPRESSIVE DISORDER",protid!=6)

##Create MAP Prior
hist_data <- data.frame(
  trial = histcontrol$nctno,
  est   = histcontrol$rslt,
  se    = histcontrol$se,
  sd    = histcontrol$sd,
  n     = histcontrol$sampsize)

dose_levels <- c(0, 2.5, 5, 10)

prior_list <- getPriorList(
  hist_data   = hist_data,
  dose_levels = dose_levels,robustify_weight = 0.5)

```

# Specifications new trial 
We will use the trial with ct.gov number NCT00635219 as exemplary new trial. 
To be able to apply the bayesian MCPMod approach, candidate models need to be specified. Since there are only 3 active dose levels we will limit the set of candidate models to a linear, an exponential and an emax model.

```{r Pre-Specification of candidate models}
#Pre-Specification (B)MCPMod 

## candidate models for MCPMod
# linear function - no guestimates needed
exp     <- DoseFinding::guesst(d     = 5,
                               p     = c(0.2),
                               model = "exponential",
                               Maxd  = max(dose_levels))
emax    <- DoseFinding::guesst(d     = 2.5,
                               p     = c(0.9),
                               model = "emax")


mods <- DoseFinding::Mods(
  linear      = NULL,
  emax        = emax,
  exponential = exp,
  doses       = dose_levels,
  maxEff      = -1,
  placEff     = -12.8)

new_trial <- filter(dataset, primtime == 8, indication == "MAJOR DEPRESSIVE DISORDER",protid==6)
n_patients <- c(150, 142, 147, 149)

```

# Combination of prior information and trial results

As outlined in citePaper, in a first step the posterior is calculated combining the prior information with the estimated results of the new trial.

```{r Trial results}
<<<<<<< HEAD
posterior <- getPosterior(prior = prior_list,
                               mu_hat = new_trial$rslt,
                               sd_hat = new_trial$se)
=======
#Simulation of new trial 
##Note: This step should not be required, as we provide summary measures directly from the new trial
data_emax <- simulateData(
  n_patients  = n_patients,
  dose_levels = dose_levels,
  sd          = attr(prior_list, "sd_tot"),
  mods        = mods,
  true_model  = "emax")

posterior <- getPosterior(prior  = prior_list,
                          data   = data_emax)

posterior <- getPosterior(prior  = prior_list,
                          mu_hat = new_trial$rslt,
                          se_hat = new_trial$se)

summary(posterior)

>>>>>>> ff9a940b072d43dcf445d6c6944d4b8bcbc07a8b
```

# Execution of Bayesian MCPMod Test step
For the execution of the testing step of bayesian MCPMod a critical value (on the probability scale) will be determined for a given alpha level. In addition a contrast matrix is created. Please note that there are different possibilities how to generate contrasts.
This information is then used as input for the bayesian MCP testing function. 

```{r Execution of Bayesian MCPMod Test step}
crit_pval <- getCritProb(
  mods           = mods,
  dose_levels    = dose_levels,
  dose_weights   = n_patients,
  alpha_crit_val = 0.1)

contr_mat_prior <- getContr(
  mods           = mods,
  dose_levels    = dose_levels,
  dose_weights   = n_patients,
  prior_list     = prior_list)

#This would be the most reasonable output, but since it is not exported it is currently not usable.
#BMCP_result<-BayesMCPi(posterior_i = posterior,
     #     contr_mat       = contr_mat_prior, 
      #    crit_prob       = crit_pval)

BMCP_result <- performBayesianMCP(
  posteriors_list = posterior,
  contr_mat       = contr_mat_prior, 
 crit_prob       = crit_pval)

# BMCP_result2 <- performBayesianMCPMod(
#     posteriors_list = posterior_emax,
#     contr_mat       = contr_mat_prior,
#     crit_prob       = crit_pval)
# 
# BMCP_result2

BMCP_result[1,1:5]
```
The testing step is significant indicating a non-flat dose-response shape. In detail the p-values for the emax model is the most significant one.

# Model fitting and visualization of results
In the model fitting step the posterior distribution is used as basis. Both simplified and full fitting are performed.
Please note that all models are fitted to the data even though they were not significant in the testing step.
For the plotting bootstrap based credible intervals (for 50% and 95%) are shown as well.

```{r Model fitting}
#Model fit
post_observed <- posterior
model_shapes  <- c("linear", "emax", "exponential")

# Option a) Simplified approach by using frequentist idea
fit_simple <- getModelFits(
  models      = model_shapes,
  dose_levels = dose_levels,
  posterior   = post_observed,
  simple      = TRUE)

# Option b) Making use of the complete posterior distribution
fit <- getModelFits(
  models      = model_shapes,
  dose_levels = dose_levels,
  posterior   = post_observed,
  simple      = FALSE)

plot(fit,cr_bands=TRUE)
plot(fit_simple, cr_bands = TRUE)

```
# Additional notes
TBD, whether certain wrapper functions should be mentioned.


