

---
title: "Simulation Example of Bayesian MCPMod for binary Data"
format: 
  html:
    fig-height: 3.5
    self-contained: true
    toc: true
    number-sections: true
    bibliography: references.bib
    code-summary: setup
    #code-fold: true
    message: false
    warning: false
vignette: >
  %\VignetteIndexEntry{Simulation Example of Bayesian MCPMod for binary Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Background and Data

In this vignette, we will show the use of the `BayesianMCPMod` R package for trial planning for binary data. 

For this setting the main specifications need to happen on the logit scale (see also add link to binary_endpoint example)

As in the [add link), we focus on the indication MDD and make use of historical data that is included in the clinDR package. 
More specifically, trial results for BRINTELLIX will be utilized to establish an informative prior for the control group.



This package makes use of the [future](https://cran.r-project.org/package=future) framework for parallel processing, which can be set up as follows:
```{r, eval = FALSE}
future::plan(future::multisession)
```


```{r setup, collapse=TRUE}
#| code-summary: setup
#| code-fold: true
#| message: false
#| warning: false

#library(BayesianMCPMod)
library(RBesT)
library(clinDR)
library(dplyr)
library(tibble)
library(reactable)

set.seed(7015)

```

```{r}
data("metaData")
testdata    <- as.data.frame(metaData)
dataset     <- filter(testdata, bname == "XELJANZ")
histcontrol <- filter(dataset, dose == 0, primtime == 12, indication == "RHEUMATOID ARTHRITIS")



hist_data <- data.frame(
  trial = histcontrol$nctno,
  est   = histcontrol$rslt,
  se    = histcontrol$se,
  sd    = histcontrol$sd,
  r     = round(histcontrol$sampsize*histcontrol$rslt),
  n     = histcontrol$sampsize)

```


```{r}
dose_levels <- c(0, 2.5, 5, 10,20)


#i) Establish MAP prior (beta mixture distribution) 
map <- gMAP(cbind(hist_data$r, hist_data$n - hist_data$r) ~ 1|histcontrol$nctno, family = binomial, tau.dist = "HalfNormal",
            tau.prior = 0.5, beta.prior = (1/sqrt(0.1*0.9)), warmup = 1000, iter = 10000, chains = 2, thin = 1)
map
prior <- automixfit(map) #fits mixture distribution from MCMC samples from above
ess(prior)

#ii) Translate prior to logit scale (to approximate via normal mixture model)
r <- rmix(prior, n=5000)
log.r <- logit(r)
approx.prior<- automixfit(log.r, type = "norm")
#Specification of reference scale 
p<-summary(prior)[1]
sigma(approx.prior)<-sqrt(1/(p*(1-p)))
ess(approx.prior)

#iii) Robustify prior 
prior.ctr<-RBesT::robustify(
      priormix = approx.prior,
      weight   = 0.2,
      sigma    = sqrt(1/(p*(1-p))))

ess(prior.ctr)

prior_trt <- RBesT::mixnorm(
    comp1 = c(w = 1, m = summary(prior.ctr)[1], n = 1),
    sigma = sqrt(1/(p*(1-p))),
    param = "mn")
  
  prior_list <- c(list(prior.ctr),
                  rep(x     = list(prior_trt),
                      times = length(dose_levels[-1])))

dose_names <- c("Ctr", paste0("DG_", seq_along(dose_levels[-1])))
names(prior_list) <- dose_names
  


```



Kindly note that a vague prior could be implemented via
```{r Setting Vague Prior Without Execution, eval = FALSE}
#prior_list_vague <- rep(list(RBesT::mixnorm(comp1 = c(w = 1, m = 0, n = 1),
              #                              sigma = sd_sim, param = "mn")),
                #        times = length(dose_levels))
#names(prior_list_vague) <- c("Ctrl", "DG_1", "DG_2", "DG_3", "DG_4")
```

# Specification of the New Trial Design 

For the hypothetical new trial, we plan with 4 active dose levels \eqn{2.5, 5, 10, 20} and we specify a broad set of potential dose-response relationships, including a linear, an exponential, an emax and 2 sigEMAX models.  
Furthermore, we assume a maximum response rate of 45% (resp. 30% on top of control) and plan a trial with 40 patients for all active groups and 30 patients for control.
Please note that the response rates need to be provided on the logit scale.

```{r}

n_patients <- c(30, 40, 40, 40, 40)

models <- Mods(linear = NULL, sigEmax = c(10,5), quadratic = -1/25, 
               logistic = c(11,15), exponential = 10, emax = 2, doses = doses,placEff = RBesT::logit(0.15),maxEff =(RBesT::logit(0.45)-RBesT::logit(0.15)))



```


# Calculation of the Success Probabilities

To calculate success probabilities for the different assumed dose-response models and the specified trial design we will apply the assessDesign function. 
We are not only interested in the success probability for the testing step, but also the assessment of the Minimally Efficacious Dose (MED). 
This effect delta is provided on the probability scale. In our case we would like to see a difference of 20% (compared to control) to claim efficacy. 

For illustration purposes, the number of simulated trial results is reduced to 100 in this example.

```{r}
success_probabilities <- assessDesign(
  n_patients  = n_patients,
  mods        = models,
  prior_list  = prior_list,
  n_sim       = 100, probability_scale=TRUE,delta          = 0.2
  ) 
```


As an alternative, we will evaluate a design with the same overall sample size but allocating more patients on the highest dose group and control.
```{r}
success_probabilities_uneq <- assessDesign(
  n_patients  = c(80, 60, 60, 60, 120),
  mods        = mods,
  prior_list  = prior_list,
  sd          = sd_tot,
  n_sim       = 100) # speed up example run-time
success_probabilities_uneq
```


